### 2012-04-05 trunk/tr-semanticsearchsurvey-data/overview.tex

\section{Semantic Search}
\begin{figure}[tbh]
	\centering
		\includegraphics[width=0.35\textwidth]{figs/semsearch.pdf}
	\label{fig:semsearch}
	\caption{Semantic Search.}
\end{figure}

Basically, \emph{search} can be characterized by three components, namely the \emph{data}, the \emph{query} and the \emph{matching framework} for computing results from the data for a given query. This is illustrated in the left portion of Fig.~\ref{fig:semsearch}. One main characteristic of concepts behind search is its emphasize on \emph{end users}. That is, search typically involves intuitive interfaces targeting users, who may do not possess knowledge about the domain, the data, and the underlying query language. The query inputs that can be obtained from these interfaces are often ambiguous. That is, they allow for many possible interpretations, which in turn, result in many possible results. Because end users are often only interested in the few best results, \emph{ranking} is considered as an essential component in search. That is, the matching framework not only specifies what constitutes matches but also their degree of matching.

\emph{Semantic search} is a concept widely used by different communities to refer to search approaches that broadly speaking, aim to \emph{use semantics to improve the search experience}. Considering the core search tasks, semantics has been used to obtain a better understanding of the data and query and to improve matching and ranking based on that (see Fig.~\ref{fig:semsearch}). There are exist different notions of semantics. One the one hand, there are proposals for using the semantics of words captured as latent concepts (e.g. to use Latent Semantic Indexing for IR \cite{DBLP:conf/sigir/Hofmann99}) or latent topics (e.g. to use Latent Dirichlet Allocation~\cite{DBLP:conf/sigir/WeiC06}). While these models only implicitly capture the semantics in terms of some latent, unknown dimensions, there are also explicit models of semantics. For instance, Explicit Semantic Analysis uses Wikipedia articles, categories, and relations between articles to capture semantics. Other explicit models of semantics (henceforth called \emph{semantic models}) include thesauri, the terminological part (TBox) of ontologies and data schemas. While these models capture semantics at the conceptual level, there are also \emph{semantic data} capturing the semantics of individual entities. To accommodate the plethora of approaches that exist, we propose the following definition of semantic search.

\begin{definition}[Semantic Search] Semantic search is a search paradigm that make uses of \emph{explicit semantics} to solve any of the \emph{core search tasks}, i.e. interpreting query and (or) data, matching and ranking. 
\end{definition}

While all existing semantic search systems use some kinds of explicit semantics, the retrieval context and the specific semantic models and data used to deal with the meaning behind the query intent and data vary.

\emph{Document Retrieval:} The IR community targets the document retrieval context where results are to be retrieved from a collection of documents. The traditional type of semantic models used here are thesauri that are employed to \emph{interpret} the terms in the textual representation of queries and data (i.e. documents). Recently, semantic data such as RDF resource descriptions have also been employed to interpret query and documents in terms of real-world entities and their relations.

\emph{Data Retrieval:} Querying entities and their relationships is a core problem in database research. As opposed to the hidden semantics of textual content in documents, information about entities and their relationships are explicitly available in this setting -- either directly as semantic data in RDF or as structured data that can be converted to RDF. Thus, understanding the semantics of the underlying data is not the problem here. However, as opposed to classic data retrieval that is based on structured query languages, intuitive query interfaces are needed in the search context. This lead to the classic search problems of interpreting the query intent and ranking the many possible results. 
%Just like in the document context, the goal here is to enable easy access to the most relevant results. Especially in the Semantic Web community, solutions targeting this problem are also referred to as semantic search because they use semantic data to interpret the query intent and to rank results.

%In this section, we establish the main dimensions in which existing solutions vary and then discussed them in more detail in the subsequent sections. 
% and then, provide a taxonomy of semantic search approaches. We focus on approaches studied by researchers in the Semantic Web community that explicitly target semantic search. Selectively, we also point out works from the IR and database communities that deal with the same problem. 
%Search is about retrieving information that are relevant with respect to a given information need. 
%Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs. 
We characterize the many different solutions along the following dimensions:

\begin{itemize}
\item the type of targeted \emph{information needs},  
\item the representation of the information need called \textit{query}, 
\item the representation of the underlying resources called \emph{data}, 
\item the \emph{semantic models} used to understand query and data, 
\item the framework for \emph{matching} queries against data, which also involves \emph{interpreting} the content and the user intent as well as \emph{ranking} the results.  
\end{itemize}

A general overview of the main types of information needs (results), queries, data, semantic models as well as interpretation, matching and ranking techniques supported by existing semantic search solutions is illustrated in Fig.~\ref{fig:semsearch_detailed}. We will now discuss existing solutions along these dimensions.

\begin{figure*}[tbh]
	\centering
		\includegraphics[width=0.85\textwidth]{figs/semsearch_detailed.pdf}
	\label{fig:semsearch_detailed}
	\caption{Overview of Semantic Search Approaches.}
\end{figure*}

\section{Information Needs}
The main motivation for semantic search is to go beyond the relatively frequent but simple queries currently supported by existing search solutions to solve the long-tail queries representing rather complex information needs. But also for simple queries, semantic data have proven to be valuable. Instead of showing documents, semantic data are used by commercial Web search engines to create rich snippets for Web pages, or to deliver direct answers.

\subsection{Entity Search} most queries on the Web asked for Web pages representing entities such as organization or people. They are used to obtain entry points, while additional navigation and browsing is still required to satisfy the actual information need. Thus, these queries are also referred to as navigational queries. Semantic data embedded in Web pages have been exploited by Google to present rich entity snippets\footnote{Google Rich Snippets} to this kind of queries. Instead of searching over a collection of documents, semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} use semantic data only, and return entity descriptions in RDF as results. Examples for this include the one asking for ``young scholars in Germany'' already mentioned before, or the query ``Researcher Thanh Tran'' depicted in the top left portion of Fig.~\ref{fig:matching}. Results for queries of this type comprise one or several entities.

\subsection{Factual Search} While results to the previous type of queries presented to the users are either some entity descriptions or Web pages about entities, the information needs behind this type of search require specific information from these descriptions and pages, respectively. Many searches on the Web for instance, aim at finding the ratings of restaurants, or the phone number of a particular person. To continue with our example, users may directly ask for ``the birth place of young scholars in Germany''. Direct answers to this type of queries are supported by WolframAlpha\footnote{\url{http://www.wolframalpha.com/}} and True Knowledge~\footnote{\url{http://www.trueknowledge.com/}}, or the various research prototypes such as Hermes~\cite{DBLP:journals/ws/TranWH09} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}. Since factual search is mostly about facts that correspond to attribute values of entities, it is often regarded as a particular type of entity search. We also do not further distinguish this from the general entity search task.

\subsection{Relational Search} The information need here goes beyond single entities and their factual information. Answers to queries of this type comprise several entities and relationships between them. Hence, processing these queries requires some understanding of relations between entities. For instance, the example presented in the introduction about 32 year old computer scientists requires knowledge about their \verb+lives in+ and \verb+birth place+ relations to some locations. Relations may be explicitly specified as part of the keyword or NL query, and entities satisfying these relation constraints can be computed using SemSearchPro~\cite{DBLP:journals/ws/TranHL11} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}. Other systems such as NAGA~\cite{DBLP:conf/icde/KasneciSIRW08} also support searches where relations to be considered are not explicitly mentioned in the query, or unknown. They address information needs that involve finding ``how some entities are related to some other entities''. The interesting part of the results here are thus not the entities, but the relationships between them -- also referred in literatures as semantic associations (direct connection) or property sequence (path)~\cite{DBLP:conf/www/AnyanwuS03}. An example for this query, asking for paths between ``Peter Mika'' and ``Thanh Tran'' is depicted in top right portion of Fig.~\ref{fig:matching}.

\section{Queries}
Typically, answering complex questions requires the expertise of technical users who know the underlying data and schema and use them to formulate questions as structured queries. However, search is commonly seen as an end-user oriented paradigm, which instead of using structured query languages, involves intuitive and easy-to use access interfaces. The there main interfaces studied for semantic search are based on keywords, NL, and facets. Often, a combination of these paradigms, e.g. keywords and facets, is used to support an iterative search process where instead of constructing the query at once, the user modifies the query and results respectively, through a series of operations.

\subsection{Keyword Search} Expressing the information needs as keywords is a paradigm that is not only popular for Web search but also widely adopted by the new breed of semantic search solutions. Most engines focusing on entity search such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} feature a keyword search interface. Keywords can also be used to formulate more complex relational searches. Addressing this scenario, engines such as Hermes~\cite{DBLP:journals/ws/TranWH09}, SemSearchPro~\cite{DBLP:journals/ws/TranHL11}, AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} and TASTIER~\cite{DBLP:conf/sigmod/LiJLF0} retrieve entities matching keywords, and search for relations between them in the data.

\subsection{NL Search} This is the other paradigm for users to express their needs using their own words. Traditionally, it has been used to formulate complex questions against expert systems built for specific domains. Recently, NL interfaces have proven to be also applicable and useful for the multiple domains setting and especially for Web search -- as demonstrated by commercial engines such as WolframAlpha and True Knowledge.

\subsection{Faceted Search} Instead of formulating the entire query at once, \emph{faceted search} supports an iterative process of querying, browsing and query refinement. Upon the initial search performed by the user (e.g. using keyword search), faceted search systems~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/semweb/FerreH11,DBLP:conf/esws/HeimEZ10} presents results as well as facets representing attributes and relations relevant for entities in the result list. These facets can then be used to browse the results and to refine or expand the initial query. While most faceted search solutions focus on browsing and refining results of entity queries, faceted search in principle can also be used to capture complex needs. For instance, gFacet\cite{DBLP:conf/esws/HeimEZ10} supports relational search through the construction of complex facet graphs representing different types of entities and relations between them.

\subsection{Iterative Search}
While faceted search is a popular paradigm, there are other similar interfaces that support an \emph{iterative search} process. Instead of showing facets as users type, also \emph{completions} of the user keywords as well as completions in the form of results matching the (possible interpretations of the) the keywords provided so far (also called result completion~\cite{DBLP:conf/esws/TranMH10}) have been presented. For instance, ESTER~\cite{DBLP:conf/sigir/BastCSW07} shows entity search results matching the keywords as well as their facets while TASTIER~\cite{DBLP:conf/sigmod/LiJLF09}, provides type-ahead search by finding complex (joins of) database tuples as the user types in query keywords. With these systems, users can iteratively construct the query by selecting the presented completions and facets. VisiNav~\cite{DBLP:journals/ws/Harth10} goes beyond this, allowing iterative query construction also via drag and drop.

\section{Data}
Data used in semantic search solutions can be broadly categorized into two types, namely \emph{semantic data} and \emph{raw data}. The latter basically comprises all representations of media objects such as audio, video and text. 
There are solutions~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TummarelloCCDDD10,DBLP:journals/ws/TranWH09}, which specifically target the data extracted from Semantic Web sources. That is, they directly operate on semantic data. In fact, structured data used in most data retrieval systems can be converted to a form that corresponds to the general notion of semantic data~\cite{DBLP:conf/sigmod/LiJLF09}. On the other hand, semantics may not be directly captured by semantic data but extracted from raw data. This is especially the case for document retrieval systems, where one of the essential task in semantic search is to obtain a semantic data representation of the documents (called \emph{semantic metadata}).

\subsection{Structured / Semantic Data}  The most common type of semantic data used in semantic search systems is RDF. Basically, RDF can be seen as a graph-structured model, representing entities, their attributes, and relations between them as a set of triples. A visual representation of such a \emph{semantic data graph} capturing information about two \verb+researcher+s with the \verb+name+s \verb+Thanh Tran+ and \verb+Peter Mika+ is depicted in the bottom portion of Fig.~\ref{fig:matching}

This general graph-structured model can be used to capture structured data of different types. In fact, most of the data made publicly available on the Web and incorporated into semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09}, Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} and Hermes~\cite{DBLP:journals/ws/TranWH09} originate from relational or XML databases. XML elements can be represented as nodes, and their structure information can be captured as edges. Likewise, information contained in tuples of a relation database can be mapped to nodes, while foreign key relationships can be modeled as edges. In fact, the conversion of XML and relational data to a RDF semantic data graph can be accomplished by using mapping rules, and there exist many standards and tools for accomplishing that (see \url{http://www.w3.org/2001/sw/rdb2rdf/}).  Represented as RDF, these and possibly other types of structured data also capture knowledge in terms of entities and their relations. Hence, especially after its conversion to RDF, structured data is often synonymously referred to as semantic data. In line with this general notion, semantic data used in semantic search systems can be defined as follows:

\begin{definition}[Semantic Data] 
Semantic data can be conceived as a graph, where nodes represent \emph{entities} and their \emph{attribute values}, and edges stand for \emph{attributes} of entities or \emph{relations} between entities. 
\end{definition}

Besides the various RDF datasets that exist on the Web, such as the hundreds of heterogeneous sources that have been made available as Linked Data~\footnote{\url{http://linkeddata.org/}}, Wikipedia can be as an extreme example that lies at one end of the spectrum of semantic data. While it is actually a collection of documents (i.e. contains mainly textual data), it fits the presented notion of semantic data because every Wikipedia page corresponds to an entity, and there are links between Wikipedia pages that can be seen as relations. In fact, exploiting this and other specific features of Wikipedia articles such as Infoboxes, a RDF dataset called DBpedia~\cite{DBLP:journals/ws/BizerLKABCH09} has been automatically derived from this collection. Wikipedia as a source of semantics is particularly popular for search systems that focus on expert search or entity search in general. It is used either to directly answer entity search queries, or as background knowledge~\cite{DBLP:conf/cikm/KapteinSVK10,DBLP:conf/cikm/BronBR10}.

On the other end of the spectrum, there are more formal views on what constitute semantic data. In particular, many researchers may argue that the reason why RDF, and other data models that are built upon a formal model of semantics, are actually called semantic data (instead of structured data) is because they can be exploited by a reasoning engine to infer new knowledge (i.e. the knowledge that is entailed by the semantics). While the formal model of semantics specified for RDF is relatively simple (consists of a few inference rules), semantic data used in existing search systems have also been represented using more expressive knowledge representation languages such as OWL and F-logic. For instance, Serene~\cite{DBLP:journals/ws/FazzingaGGL11} makes use of facts that are captured as Abox assertions of an OWL ontology, while ORAKEL~\cite{DBLP:journals/dke/CimianoHHMS08} search over an F-logic knowledge base. However, while the use of formal semantics and reasoning has been investigated, they play only a limited role in existing systems. The 
majority of approaches does not rely on reasoning. It seems that the research focus still lies in correctly understanding the ambiguous queries and data (namely, to interpret queries and data as elements of the semantic data model as defined above), while reasoning over semantic data is beneficial but not essential yet.

Accordingly, a general notion of semantic data is employed in this work to consider all those systems, which consider the semantics of entities and relations but may not have a formal model of semantics available, or does not exploit it for search.

\begin{figure}[thb]
	\centering
		\includegraphics[width=0.5\textwidth]{figs/matching.pdf}
	\label{fig:matching}
	\caption{Examples for semantic data, queries and matching techniques.}
\end{figure}

\subsection{Raw Data and Semantic Metadata} There are engines directly operating on semantic data to provide direct answers (data retrieval systems). These are mainly systems, which provide search interfaces over structured databases that have been converted to semantic data graphs~\cite{DBLP:conf/sigmod/LiJLF09,DBLP:conf/sigmod/LiOFWZ08}, or RDF data and ontologies crawled from the Semantic web~\cite{DBLP:journals/ijswis/ChengQ09,DBLP:journals/ws/TranWH09,DBLP:journals/ws/HoganHUKPD11}. Besides them, there are also semantic search systems supporting the retrieval of documents or media objects in general. They employ semantic metadata, often in combination with the raw data representation of these objects. Basically, semantic metadata is semantic data that captures information about the objects to be retrieved. Because it is clear from the context, these terms are often used synonymously (in this work). Metadata includes basic information about the objects such as \verb+author+ and \verb+year+. One main challenge in semantic search is to interpret the semantics behind the content captured as raw data and to represent it as semantic metadata. For instance, the content of a document may be recognized as referring to a \verb+meeting+ with the two \verb+researcher+s \verb+Peter Mika+ and \verb+Thanh Tran+ as \verb+participant+s. Semantic metadata representing the content may also be manually produced and embedded into the objects. Recently, several industry projects such as Google Rich Snippets and Yahoo! SearchMonkey actively target this development, providing incentives for site owners to embed RDFa or other kind of semantic metadata into their Web pages. Note that while we discussed how to conceive Wikipedia as semantic data (with pages corresponding to entities), a more typical viewpoint is to consider it as a collection of documents that are manually associated with metadata: every page is associated with a set of categories and exactly one entity (the entity it is about).

While the amount of available metadata is increasing, it is still too sparse to cover all information needs. Thus, metadata is mostly used as additional information that can help to improve standard search over raw data~\cite{DBLP:journals/tkde/CastellsFV07,DBLP:journals/ws/FernandezCLVCM11}. Search over raw data can also be seen as a fall-back solution for cases where metadata cannot completely satisfy the information need. There exists also proposals for ontology-based IR, which completely rely on metadata~\cite{tran2007expressive}. In this case the retrieval of documents is formulated as a data retrieval task, where data about the documents (metadata) is returned as a direct answer.

>>>>

\section{Semantic Search}\label{sec:ss}

\begin{figure}
	\centering
		\includegraphics[width=0.35\textwidth]{figs/semsearch.pdf}
	\caption{Semantic Search.}
	\label{fig:semsearch}
\end{figure}

Basically, \emph{search} can be characterized by three components, namely the \emph{data}, the \emph{query} and the \emph{matching} framework for computing results from the data for a given query. This is illustrated in the left portion of Fig.~\ref{fig:semsearch}. One main characteristic of search concepts is its emphasize on end users. That is, search typically involves intuitive interfaces targeting users, who may do not possess knowledge about the domain, the data and structured query languages. The query inputs that can be obtained from these interfaces are often ambiguous. That is, they allow for many possible \emph{interpretation}s, which in turn, yield many possible results that vary in relevance w.r.t.~ the intended query intent. 
% Because end users are often only interested in the few best results, 
\emph{Ranking} is an essential component in search that aims to address this, i.e. to distinguish results in terms of relevance. Basically, matching can be conceived as the task of identifying matches whereas ranking is more specifically about the degree of matching.

\emph{Semantic search} is a concept widely used by different communities to refer to search approaches that broadly speaking, use semantics to improve the search experience. Considering the core search tasks, semantics has been used to obtain a better understanding of the data and query as well as to improve matching and ranking based on that (see Fig.~\ref{fig:semsearch}). There are exist different notions of semantics. One the one hand, there are proposals for using the semantics of words captured as latent concepts (e.g. inferred through Latent Semantic Indexing~\cite{DBLP:conf/sigir/Hofmann99}) or latent topics (e.g. inferred through Latent Dirichlet Allocation~\cite{DBLP:conf/sigir/WeiC06}). While these models only implicitly capture the semantics in terms of some latent, unknown dimensions, there are also explicit models of semantics. For instance, Explicit Semantic Analysis uses Wikipedia articles, categories, and relations between articles to capture semantics in terms concepts, which are then used for concept-based IR~\cite{DBLP:journals/tois/EgoziMG11}. Other explicit models of semantics (henceforth called \emph{semantic models}) include thesauri, the terminological part (TBox) of ontologies and data schemas. While these models capture semantics at the conceptual level, there are also \emph{semantic data} capturing the semantics of individual entities. To accommodate the wide range of semantic search approaches that exist, we formulate the following general notion of semantic search:

\begin{definition} \emph{Semantic search} is a search paradigm that makes use of explicit semantics to solve core search tasks, i.e. to use semantics for interpreting query and data, matching query against data and ranking results. 
\end{definition}

While all semantic search approaches involve some kinds of explicit semantics, the retrieval contexts and the specific semantic models used to deal with the meaning behind the query intent and data vary. In particular, we identified the following aspects, based on which we will characterize and distinguish existing solutions:

\begin{itemize}
\item the type of targeted \emph{information needs},  
\item the representation of information resources (\emph{data}), 
\item the representation of the information need (\textit{query}) or respectively, the underlying method for querying the data (querying paradigms), 
\item the \emph{semantic models} used to understand and to represent the meaning behind query and data, 
\item the framework for \emph{matching} queries against data, which also involves \emph{interpreting} the data and query intent as well as \emph{ranking} the results.  
\end{itemize}

For instance, we can look at the differences in the data to arrive at the distinction between document retrieval and data retrieval, two major research directions in search that mark the borders of large communities.

\textbf{Document Retrieval:} The IR community targets the document retrieval context where results are retrieved from a collection of documents (primarily textual data). Semantic search of this type is different from standard document retrieval approaches in the use of semantics. The traditional type of semantic models used here are thesauri that are employed to interpret the terms in the textual representation of queries and data. Recently, semantic data such as RDF resource descriptions have also been employed to interpret query and documents in terms of real-world entities and their relations.

\textbf{Data Retrieval:} Querying entities and their relations is a core problem in database research. As opposed to the hidden semantics of textual content in documents, information about entities and their relations are explicitly available in this setting -- either directly as semantic data in RDF or as some kinds of structured data that can be converted to RDF. Thus, understanding the semantics of the underlying data is not the problem here. However, as opposed to standard data retrieval that is based on structured query languages, intuitive query interfaces are needed in the search context. This leads to the issue of ambiguity. Hence, semantic search approaches of this type have to deal with the resulting problems of interpreting the query intent and ranking the many possible results. 
%Just like in the document context, the goal here is to enable easy access to the most relevant results. Especially in the Semantic Web community, solutions targeting this problem are also referred to as semantic search because they use semantic data to interpret the query intent and to rank results.

%In this section, we establish the main dimensions in which existing solutions vary and then discussed them in more detail in the subsequent sections. 
% and then, provide a taxonomy of semantic search approaches. We focus on approaches studied by researchers in the Semantic Web community that explicitly target semantic search. Selectively, we also point out works from the IR and database communities that deal with the same problem. 
%Search is about retrieving information that are relevant with respect to a given information need. 
%Generally speaking, approaches that fall under the category of \emph{semantic search} use semantic data for representing information and (or) semantic models for interpreting the data and information needs.

More fine-grained than this general breakdown into document and data retrieval, Fig.~\ref{fig:semsearch_detailed} illustrates the specific differences in queries, data, semantics, results (corresponding to information needs) and solutions for the subproblems that distinguish existing semantic search approaches. We can see that central to semantic search is the use of semantics (depicted as gray boxes in Fig.~\ref{fig:semsearch_detailed}). In particular, semantic resources represented by lexical models, knowledge models as well as semantic data and metadata are used for the subproblems of understanding raw data (e.g. text) and queries. The resulting semantics of data and queries are then employed for solving the subproblems of matching and ranking.

%We will now discuss them along these aspects.

\begin{figure*}[tbh]
	\centering
		\includegraphics[width=0.75\textwidth]{figs/semsearch_detailed}
	\caption{Overview of Semantic Search Approaches.}
	\label{fig:semsearch_detailed}
\end{figure*}

\section{Information Needs}\label{sec:needs}

The main motivation for semantic search is to go beyond the relatively frequent but simple queries currently supported by existing Web search solutions to solve the long-tail queries representing rather complex information needs. But also for simple queries, semantic data have proven to be valuable. Instead of showing documents, semantic data are used by commercial Web search engines to create rich snippets for Web pages, or to deliver direct answers, e.g a specific address for a query mentioning ``location'' and a named entity such as ``Yahoo! Research Lab Barcelona''. We will now discuss several common types of queries and the information needs behind them, from the more simple entity queries to complex relational and analytical queries.

\subsection{Entity Search} Most queries on the Web ask for pages representing entities such as companies or people. They are used to obtain entry points, while additional navigation and browsing are still required to satisfy the actual information need. Thus, in the IR context, these queries are also referred to as navigational queries. Recently, semantic data embedded in Web pages have been exploited to address this type of queries. This was pioneered by Yahoo! in their SearchMonkey program, and later adopted by Google to present rich entity snippets\footnote{Google Rich Snippets} as answers to this kind of queries. As an example, Fig.~\ref{fig:semantic_layer} illustrates the entity search functionalities provided by Yahoo!. Not only there are Web pages but also entity descriptions appear as results. These descriptions are directly retrieved from semantic data (in this case, a dataset about music artists and their albums). Instead of searching over a collection of documents, semantic search engines such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} use semantic data only, and return entity descriptions in RDF as results. Examples for this type of queries include the one asking for ``young scholars in Germany'' already mentioned before, or the query ``Researcher Thanh Tran'' depicted in the top left portion of Fig.~\ref{fig:matching}. Results for queries of this type comprise one or several entities.

\subsection{Factual Search} While results to the previous type of queries presented to the users are either some entity descriptions or Web pages about entities, the information needs behind this type of search requests require specific information from these descriptions and pages, respectively. Many searches on the Web for instance, aim at finding the ratings of restaurants, or the phone number of a particular person. To continue with our example, users may directly ask for ``the birth place of young scholars in Germany''. Direct answers to this type of queries are supported by WolframAlpha\footnote{\url{http://www.wolframalpha.com/}} and True Knowledge\footnote{\url{http://www.trueknowledge.com/}}, or the various research prototypes such as Hermes~\cite{DBLP:journals/ws/TranWH09} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}. Since factual search is mostly about facts that correspond to attribute values of entities, it is often regarded as a particular type of entity search. In this survey, we do not further distinguish this from the general entity search task.

\subsection{Relational Search} The information need here goes beyond single entities and their factual information. Answers to queries of this type comprise several entities and relationships between them. Hence, processing these queries requires some understanding of relations between entities. For instance, the example presented in the introduction about 32 year old computer scientists requires knowledge about their \verb+lives in+ and \verb+birth place+ relations to some locations. Relations may be explicitly specified as part of the keyword or NL query, and entities satisfying these relation constraints can be computed using SemSearchPro~\cite{DBLP:journals/ws/TranHL11} or AquaLog~\cite{DBLP:journals/ws/LopezUMP07}.

Other systems such as NAGA~\cite{DBLP:conf/icde/KasneciSIRW08} also support searches where relations to be considered are not explicitly mentioned in the query, or simply \emph{unknown}. They address information needs that involve finding how some entities are related to some other entities. The interesting part of the results here are thus not the entities, but the relationships between them -- also referred in literatures as semantic associations (direct connection) or property sequences (indirect connections, i.e. path)~\cite{DBLP:conf/www/AnyanwuS03}. An example for this type of query asking for paths between ``Peter Mika'' and ``Thanh Tran'' is depicted in the top right portion of Fig.~\ref{fig:matching}.

Even though Yahoo! entity search as shown in Fig.~\ref{fig:screenshot_yahoo} does not directly search for relations, it can be seen on the left portion that relations between entities captured in semantic data constitute valuable information for suggesting related entities. Searching for known relations or unknown relations is supported by the Information Workbench\footnote{\url{http://iwb.fluidops.com}}, a commercial adoption of SemSearchPro. On the bottom part of Fig.~\cite{fig:screenshot_iwb}, we can see results returned to a query that specifically asks for entities connected through the \verb+producer+ relation. When relations are not explicitly given in the query but only entities and (or) concepts, this system is also able to explore paths between them. However, this system does not directly return relationships and paths in the data as results, but structured queries representing interpretations of the entered keywords -- a querying paradigm we will discuss in the next section.

\subsection{Analytical Search}
Beyond the common searches for entities and relations, which form the focus of this survey, there are also information needs, which can only be addressed when some additional analyses are performed on top of the data. Generally speaking, any kind of additional computation may be applied to the data and results for the purpose of analytical search. Analytics often found in semantic search engines are supported through simple sorting and averaging, more sophisticated statistical and mathematical models, or some form of Machine Learning based inductive reasoning or logic-based deductive reasoning. For instance, WolframAlpha is advertised as a computation engine because it applies different kinds of mathematical models to compute answers to queries, whereas True Knowledge uses an inference engine to perform temporal and geospatial reasoning.

\begin{figure}
	\centering
		\includegraphics[width=0.5\textwidth]{figs/screenshot_yahoo}
	\caption{Entity search with Yahoo!.}
	\label{fig:screenshot_yahoo}
\end{figure}

\section{Querying Paradigms}\label{sec:querying}
Typically, addressing complex needs requires the expertise of technical users who know the underlying data and schema and use them to formulate questions as structured queries. However, search is commonly seen as an end-user oriented paradigm, which instead of using structured query languages, involves intuitive and easy-to use access interfaces. The three main interfaces studied for semantic search are based on keywords, NL, and facets. Often, a combination of these paradigms, e.g. keywords and facets, is used to support an iterative search process where instead of constructing the query at once, the user modifies the query and results respectively, through a series of operations.

\subsection{Keyword Search} Expressing the information needs as keywords is a paradigm that is not only popular for Web search but also widely adopted by the new breed of semantic search solutions. Most engines focusing on entity search such as Falcons~\cite{DBLP:journals/ijswis/ChengQ09} and Sig.ma~\cite{DBLP:journals/ws/TummarelloCCDDD10} feature a keyword search interface. Keywords can also be used to formulate more complex relational searches. Addressing this scenario, engines such as Hermes~\cite{DBLP:journals/ws/TranWH09}, SemSearchPro~\cite{DBLP:journals/ws/TranHL11}, TASTIER~\cite{DBLP:conf/sigmod/LiJLF0} and IBM's AVATAR~\cite{DBLP:conf/sigmod/KandoganKRVZ06} retrieve entities matching keywords, and search for relations between them in the data.

\subsection{NL Search} This is the other paradigm for users to express their needs using their own words. Traditionally, it has been used to pose complex questions against expert systems built for specific domains. Recently, NL interfaces have proven to be also applicable and useful for the multiple domains setting and especially for Web search -- as demonstrated by commercial engines such as WolframAlpha, True Knowledge and Apple's Siri\footnote{\url{http://en.wikipedia.org/wiki/Siri_(software)}}.

\subsection{Faceted Search} Instead of formulating the entire query at once, \emph{faceted search} supports an iterative process of querying, browsing and query refinement. This belongs to the broader category of approaches called \emph{exploratory search}, which assumes that users do not precisely know how or what to search and thus, combines querying and browsing strategies to enable learning and investigation. Upon the initial search performed by the user (e.g. using keyword search), faceted search systems~\cite{DBLP:conf/dexa/WagnerLT11,DBLP:conf/semweb/FerreH11,DBLP:conf/esws/HeimEZ10} present results as well as facets representing attributes and relations that are applicable for refining (or simply, are related to) the current results. These facets can then be used to browse, to refine or to expand the results (i.e. to modify the query, respectively). Microsoft's EntityCube\footnote{\url{http://entitycube.research.microsoft.com/}} for instance, returns entities upon users' keyword search requests along with relations and attributes of these entity results as facets. Parallax\footnote{\url{http://www.freebase.com/labs/parallax/}} is another commercial faceted search solution (from Freebase, now Google) that enables a combination of search, intelligent result visualization and facet-based browsing.

While most faceted search solutions focus on browsing and refining results of entity queries, faceted search in principle can also be used to address complex needs. For instance, gFacet~\cite{DBLP:conf/esws/HeimEZ10} supports relational search through the construction of complex facet graphs representing different types of entities and relations between them. Fig.~\ref{fig:screenshot_iwb} shows the faceted search feature from the Information Workbench. Every column in the result table captures one particular type of entities and this system shows facets for every type that appears in the results (e.g. Fig.~\ref{fig:screenshot_iwb} shows facets for column 1). Hence, entries in every column (representing a partial result and a query part, respectively) can be refined or expanded. For instance, the column of singles shown in Fig.~\ref{fig:screenshot_iwb} can be further refined to contain only those connected with \verb+Freddie Mercury+ through the \verb+writer+ relation.

\subsection{Iterative / Exploratory Search} 
While faceted search is the most popular paradigm in the industry, there are other exploratory search interfaces that support an \emph{iterative search} process. Instead of showing facets as users type, also \emph{completions} of the single user keywords (term completions) or of the entire query representing the full query intent (query completions) have been proposed. One example system supporting this is the Information Workbench shown in Fig.~\ref{fig:screenshot_iwb}, which presents terms matching the current tokens entered by the users, as well as full interpretations of the entire query. For ``queen single'', the interpretations shown indicate that the query intent may be something matching the word ``queen'' that is of the type \verb+single+, or something that is of the type \verb+single+, which is produced (or written) by something else matching the word ``queen''. Google, Freebase\footnote{\url{http://www.freebase.com/docs/suggest}} and True Knowledge also present possible interpretations of the query as the user type or after issuing a query.

Instead query-based completions, also results matching the (possible interpretations of the) keywords provided so far have been presented (called result completions~\cite{DBLP:conf/esws/TranMH10}). For instance, ESTER~\cite{DBLP:conf/sigir/BastCSW07} shows entity search results matching the keywords as well as their facets (see CompleteSearch~\footnote{\url{http://www.dblp.org/search/index.php}}, which is an adoption of ESTER) whereas TASTIER~\cite{DBLP:conf/sigmod/LiJLF09} provides type-ahead search by finding complex (joins of) database tuples as the user types query keywords. With these systems, users can iteratively construct the query by selecting the presented completions and facets. VisiNav~\cite{DBLP:journals/ws/Harth10} goes beyond this selection-based interaction, allowing iterative query construction also via drag and drop.

\begin{figure}
	\centering
		\includegraphics[width=0.5\textwidth]{figs/screenshot_iwb}
	\caption{Querying with the Information Workbench.}
	\label{fig:screenshot_iwb}
\end{figure}

\section{Data}\label{sec:data}
The information resources made available for search as well as any kind of additional background information used to improve the search experience, are kept and managed by the system as data. In semantic search solutions, data can be broadly categorized into two types, namely \emph{semantic data} and \emph{raw data}.

Basically, semantic data describe real-world objects in terms of entities and their relations. Primarily, semantic data have been used to refer to RDF datasets, or instance data contained in ontologies represented in Semantic Web languages such as OWL (the Web Ontology Language, a logic-based W3C standard\footnote{http://www.w3.org/TR/owl-features/} for representing the semantics of vocabulary / schema elements) and RIF (the Rule Interchange Format, a W3C standard for representing and exchanging rules). However, different kinds of structured data actually correspond to this rather general notion of semantic data. In fact, large amounts of structured data formerly kept in hidden 
%XML or relational 
Web databases 
have been converted to and published on the Web as RDF data. Several semantic search systems have been built that specifically target the retrieval of semantic data. Instead of searching directly over semantic data, classic retrieval systems search over a raw data representation of information objects such as audios, videos, images and texts. For instance, document retrieval systems search for textual documents that are represented as bags of words. As opposed to semantic data, raw data do not explicitly capture the semantics of information resources in terms of entities and their relations. Thus, for supporting document (or image, video or audio) retrieval as semantic search, one core subtask is the recognition of named entity in the raw text. Named entity recognition and other data interpretation tasks such as relation extraction are performed to obtain a semantic data representation of raw data (also called \emph{semantic metadata}).

\subsection{Semantic Data}  The most common type of semantic data used in semantic search systems is RDF. Basically, RDF is a graph-structured model, representing entities, their attributes, and relations between them as a set of triples. A visual illustration of such a \emph{semantic data graph} capturing information about two \verb+researcher+s, whose \verb+names+ are \verb+Thanh Tran+ and \verb+Peter Mika+, is depicted in the bottom portion of Fig.~\ref{fig:matching}
